Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/wg_appendix_best_practices.tex
Fix typos.
Section 5.1 and Appendix D: touched up.

Core questions that will need to be explored are in reliability (reproducibility), usability, extensibility, knowledge management and continuity (transitions between people). Answers to these will guide us on how a software tool becomes part of the core workflow of well identified users (stakeholders) relating to tool success and hence sustainability.
%\katznote{prev sentence is complex and awkward} % see fix
Ideas that may need to be explored include:
\begin{itemize}

@@

The opportunity lies in collaboration on a white paper, which will be revisited
regularly for further improvements, to enhance knowledge of the state of best
practices, resulting in a peer-reviewed paper. We would like to reach a wide
community by doing this. But these are also the challenges and obstacles -- to
get everyone to contribute to the paper and to reach the community.

\noindent{\bf White Paper Outline:}
\begin{enumerate}
\item Introduction and Scope of White Paper 
\item Related Work
\item Case Studies
\begin{enumerate} 
\item PeTSC
\item NWChem
\item CIG
\end{enumerate}
\item Community Related Practices
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Governance and management
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Funding Related
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Metrics for sustainability
\item Tools
\item Conclusions
\end{enumerate}

>>>>

Core questions that will need to be explored are in reliability,
reproducibility, usability, extensibility, knowledge management, and continuity
(transitions between people). Answers to these will guide us on how a software
tool becomes part of the core workflow of well identified users (stakeholders)
relating to tool success and hence sustainability.
%\katznote{prev sentence is complex and awkward} % see fix
Ideas that may need to be explored include:
\begin{itemize}

@@

There is an opportunity to collaborate on a white paper, which will be revisited
regularly for further improvements, to enhance knowledge of the state of best
practices, resulting in a peer-reviewed paper. We would like to reach a wide
community by doing this. But these are also the challenges and obstacles -- to
get everyone to contribute to the paper and to reach the community.

\medskip
\noindent{\bf White Paper Outline:}
\begin{enumerate}
\item Introduction and Scope of White Paper 
\item Related Work
\item Case Studies
\begin{enumerate} 
\item PETSc
\item NWChem
\item CIG
\end{enumerate}
\item Community Related Practices
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Governance and management
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Funding Related
\begin{enumerate} 
\item Findings
\item Recommendations
\end{enumerate}
\item Metrics for sustainability
\item Tools
\item Conclusions
\end{enumerate}
